How Removing a Ranked Climber Changes the Winners

### 2021-08-04 R/remove_climber_sim.Rmd
update remove1 sims + add tokyo2020 qualification data

as can be seen, the probability is relatively low when the 9th place competitor is removed. My hypothesis is that there is enough separation between the original finalists and the 10th+ ranking competitors in the individual events that there isn't a high chance that the total rankings of the finalists can be overtaken by 10+th place competitors. Note: it might be worth computing the probability of getting a low ranking in any of the individual events, given that a competitor is a finalist.

@@

remove_c5 <- lapply(5:20, function(x) replicate(100, displace_climber(nsim = 100, drop_rank = 5, nc = x)))

remove_c5_df <- lapply(5:20
                  , function(x) {
                    data.frame(n_climbers = x
                               , dropped_rank = 5
                               , displ_prob = remove_c4[[x-4]]
                               )
                    }
                  ) %>%
  do.call(rbind, .)
#save(remove_c5_df, "R/remove_c5_sims.rdata")
```

### Removing 4th Place
```{r, echo = FALSE}
load("remove_c4_sims.rdata")
remove_c4_df %>%
  ggplot(aes(x = n_climbers, y = displ_prob)) +
  geom_boxplot(aes(group = n_climbers)) +
  theme_minimal() +
  ylab("Probability of Displacing Top 3") +
  xlab("Number of Original Climbers")
```

# Questions: 
- How often would a finalist be replaced
- How often does someone who wasn't a medalist before become a medalist 
- How often do we see a flip (two consecutive climbers switch places), jump (a climber jumps up more than one rank), drop (a climber drops down more than one rank)
- how do the simulations compare to doing the same with actual data?

>>>>

as can be seen, the probability is relatively low when the 9th place competitor is removed. My hypothesis is that there is enough separation between the original finalists and the 10th+ ranking competitors in the individual events that there isn't a high chance that the total rankings of the finalists can be overtaken by 10+th place competitors. Note: it might be worth computing the probability of getting a low ranking in any of the individual events, given that a competitor is a finalist (ie: $P(r_1 > 8 \text{ or } r_2 > 8 \text{ or } r_3 > 8 \text{ }|\text{ } R_T \leq 8)$).

@@

remove_c5 <- lapply(5:20, function(x) replicate(100, displace_medalist(nsim = 100, drop_rank = 5, nc = x)))

remove_c5_df <- lapply(5:20
                  , function(x) {
                    data.frame(n_climbers = x
                               , dropped_rank = 5
                               , displ_prob = remove_c5[[x-4]]
                               )
                    }
                  ) %>%
  do.call(rbind, .)
#save(remove_c5_df, file = "R/remove_c5_sims.rdata")

remove_c6 <- lapply(6:20, function(x) replicate(100, displace_medalist(nsim = 100, drop_rank = 6, nc = x)))
remove_c6_df <- lapply(6:20
                  , function(x) {
                    data.frame(n_climbers = x
                               , dropped_rank = 6
                               , displ_prob = remove_c6[[x-5]]
                               )
                    }
                  ) %>%
  do.call(rbind, .)
```

### Removing 4th Place
```{r, include=FALSE}
load("remove_c4_sims.rdata")
remove_c4_df %>%
  ggplot(aes(x = n_climbers, y = displ_prob)) +
  geom_boxplot(aes(group = n_climbers)) +
  theme_minimal() +
  ylab("Probability of Displacing Top 3") +
  xlab("Number of Original Climbers")
```

```{r, echo = FALSE}
load("remove_c5_sims.rdata")
load("remove_c6_sims.rdata")
remove_c456 <- rbind(remove_c4_df, remove_c5_df, remove_c6_df)
remove_c456 %>%
  group_by(n_climbers, dropped_rank) %>%
  summarize(av_disp_prob = mean(displ_prob)) %>%
  ggplot(aes(x = n_climbers, y = av_disp_prob)) +
  geom_line(aes(color = as.factor(dropped_rank))) +
  theme_minimal()
```

# Questions: 
- How often do we see a flip (two consecutive climbers switch places), jump (a climber jumps up more than one rank), drop (a climber drops down more than one rank)
- how do the simulations compare to doing the same with actual data?
